Attempting to write a full model

### 2016-09-14 R/misc/fullModel.rmd
almost done

makeMutMat <- function(xpars) {
    p <- with(xpars, {
        p <- matrix(NA, n.alpha, n.alpha)
        for(i in 1:n.alpha){
            x <- min.alpha + (i-1)*d.alpha
            denom <- 
                diff(pnorm(c(min.alpha-d.alpha/2,max.alpha+d.alpha/2),
                    mean=x, sd=Vm))
            for (j in 1:n.alpha){
                k <- min.alpha + (j-1)*d.alpha
                p[i,j] = diff(pnorm(k + c(-1,1)*d.alpha/2, mean = x, sd = Vm))/denom
            }
        }
    p
    })
    return(p)
}

@@

    #infection
    if(infection){
        p <- makeMutMat(parameters)

        beta.SI <- matrix(rep(Beta, n.risk*n.risk), nrow = n.risk, byrow = TRUE)

@@

            if(infection){
                ##within couple infection
                inf.SI.from <- beta.SI * SI
                inf.SI.tmp <- distribute.SIinf(inf.SI.from)
                inf.SI.to <- inf.SI.tmp + t(inf.SI.tmp)
                diag(inf.SI.to) <- diag(inf.SI.to)/2

@@

                ce.mut <- inf.ce.tmp %*% p
                inf.SS.tmp2 <- outer(c(t(r.risk * SS_adj)), c(ce.mut))
                inf.SS.to <- matrix(c(t(inf.SS.tmp2)), nrow = n.risk, byrow = TRUE)

@@

            dS <- - rho2 * S + colSums(cc_mat * SS_adj) + rowSums(d.SI) - inf.S.from + mort.I.sus +
                mort.SI.sus + mort.II.sus
            dI <- - rho2.I * I + colSums(d.SI) + colSums(cc_mat.II * II_adj) + inf.S.to - mort.I.out + mort.II.I
            dSS <- f.SS - d.SS - inf.SS.from
            dSI <- f.SI - d.SI - inf.SI.from + inf.SS.to - inf.SI.from2 - mort.SI.out
            dII <- f.II - cc_mat.II * II + inf.SI.to + inf.SI.to2 - mort.II.out

@@

            list(c(dS, dI, dSS, dSI, dII), tot_I = tot_I, mean_V = tot_V/tot_I)
        })
    }
}

@@

Seems like this model works?

>>>>

@@

    #infection
    if(infection){
        beta.SI <- matrix(rep(Beta, n.risk*n.risk), nrow = n.risk, byrow = TRUE)

@@

            if(infection){
                ##within couple infection
                inf.SI.from <- beta.SI * SI

                inf.SI.tmp <- distribute.SIinf(inf.SI.from)
                inf.SI.to <- inf.SI.tmp + t(inf.SI.tmp)
                diag(inf.SI.to) <- diag(inf.SI.to)/2

@@

                ce.mut <- inf.ce.tmp %*% p
                inf.SS.tmp2 <- outer(c((r.risk * SS_adj)), c(ce.mut))
                inf.SS.to <- matrix(c(t(inf.SS.tmp2)), nrow = n.risk, byrow = TRUE)

@@

            dS <- - rho2 * S + colSums(cc_mat * SS_adj) + rowSums(d.SI) - inf.S.from + mort.I.sus +
                mort.SI.sus + mort.II.sus

            dI <- - rho2.I * I + colSums(d.SI) + colSums(cc_mat.II * II_adj) + inf.S.to - mort.I.out + mort.II.I
            dSS <- f.SS - d.SS - inf.SS.from
            dSI <- f.SI - d.SI - inf.SI.from + inf.SS.to - inf.SI.from2 - mort.SI.out
            dII <- f.II - cc_mat.II * II + inf.SI.to + inf.SI.to2 - mort.II.out

@@

            list(c(dS, dI, dSS, dSI, dII), 
            		 ##tot_I = tot_I, mean_V = tot_V/tot_I
            		 inf.SI.to2)
        })
    }
}

@@

Seems like this model works? Now, let's test rcpp function...

```{r rcpp}
library(Rcpp)
sourceCpp("fullModel.cpp")

r1 <- lsoda(unlist(yini1), func = model1(HIVpars.mean), parms = HIVpars.mean, times = tvec)
r1rcpp <- lsoda(unlist(yini1), func = g, parms = expand(HIVpars.mean), times = tvec)
yini2 <- list(N = c(0.1, 0.2, 0.3), NN = matrix(c(0.1, 0.1, 0, 0,0,0,0,0,0), 3, 3))
yini3 <- calc_yini_full(HIVpars.mean)
library(microbenchmark)
##length(unlist(yini3)) = 4233
yini4 <- rnorm(4233)

microbenchmark(
tmpa = c(unname(g2(0, unlist(yini4), expand(HIVpars.mean))$dI)),
tmpb = c(unname(model2(expand(HIVpars.mean), infection = TRUE, mortality = TRUE)(0, unlist(yini4), expand(HIVpars.mean))[[1]][4:66]))
)
##1:3, 4:66. 67:75, 76:264
##-c(1:264)
all.equal(tmpa, tmpb)
plot(tmpa)
plot(tmpb)
```

InfSIto
